---
title: "runr"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=TRUE, comment=NA)
```

> `runr` packs a set of higher order functions for running lists of functions in various modes.

+ [runSeries]
+ [runWaterfall]
+ [runRace]
+ [runParallel]

***

### runSeries

`runr::runSeries` runs its input tasks sequentially returning either a named list (on error `NULL`) or the value of a given callback.

`runr::runSeries(tasks = list(NULL), cb = NULL)`

```{r}
# some fictional workers
moo <- function() 'moooo'
zoo <- function() 1L:3L
# callback skeleton - must have exactly two parameters
callback <- function(err, d) if (is.null(err)) d else stop(err, err$task)
# run!
runr::runSeries(list(moo, zoo, function() 1L), callback)
 ```
Input functions can be anonymous or named. 

***
 
### runWaterfall

`runr::runWaterfall` runs its input tasks sequentially, passing each task's return value to the next task, and returns either a named list (on error `NULL`) or the value of a given callback.

All tasks except the first must have at least one parameter :ocean:

`runr::runWaterfall(tasks = list(NULL), cb = NULL)`

```{r}
# chain/pipe consecutive returns
runr::runWaterfall(list(zoo,
                        base::factorial,  # reference names anyhow
                        runr::bind(Reduce, function(a, b) a + b)))  # binding
```

`runr::bind` takes a function object and a variable sequence of parameters as inputs and returns a closure with the given parameters bound to it.

***

### runRace

`runr::runRace` runs its input tasks parallel until the very first return of any of its tasks and returns either a named list (all `NULL` but one and on error `NULL`) or the value of a given callback.

*Currently `runr::bind` can neither be used in conjunction with `runr::runRace` nor `runr::runParallel` because each input task to the latter pair is run in a separate child process...not a big deal...might get a fix.*

`runr::runRace(tasks = list(NULL), cb = NULL)`

```{r}
# see how return is variable due to instable time lags between child launches
runr::runRace(list(function() {Sys.sleep(11L); '1st first'}, 
                   function() {Sys.sleep(10L); '2nd first'}), 
              callback)
```

***

### runParallel

`runr::runParallel` runs its input tasks parallel until all complete and returns either a named list (on error `NULL`) or the value of a given callback.

`runr::runParallel(tasks = list(NULL), cb = NULL)`

```{r}
stalk <- function() {                   # io sth
  jsonlite::fromJSON('https://api.github.com/users/chiefBiiko')$hireable
}
emph <- function(n=10L) strrep('!', n)  # do sth
hireme <- function(err, d) {            # callback
  if (!is.null(err)) stop(err, err$task)  # check n go
  sprintf('dev: @chiefBiiko | hireable: %s%s | %s',
          as.character(d$function1),
          d$function2,
          d$function3)
}
# see ya!
runr::runParallel(list(stalk,
                       emph,
                       function() {
                         Sys.sleep(3.6)
                         gsub('[^3<]', '', '<kreuzberg36original>')
                       }),
                  hireme)
```
