---
title: "runr"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=TRUE, comment=NA)
```

`runr` packs a set of higher order functions for running lists of functions in various modes.

:movie_camera: *[runSeries]* 

:ocean: *[runWaterfall]* 

:running: *[runRace]* 

:100: *[runParallel]*

***

### Get it

```{r, eval=F}
devtools::install_github('chiefBiiko/runr')
```

***

### API

`runr::runSeries(tasks = list(NULL), cb = NULL)`

+ `tasks` List of functions **required** 
+ `cb` Function with signature `cb(error, data)` **optional**

***

Values for the `tasks` or `cb` parameter can be defined anonymous or referenced to via a valid function name. Specifying a callback allows easy exception handling.

## runSeries

`runr::runSeries` runs its input tasks sequentially returning either a named list (on error `NULL`) or the value of a given callback.

```{r}
# some setup
moo <- function() 'moooo'
zoo <- function() 1L:3L
# callback skeleton - must have exactly two parameters
callback <- function(err, d) if (is.null(err)) d else stop(err, err$task)

# run!
runr::runSeries(list(moo, zoo, function() 1L), callback)
 ```

***
 
## runWaterfall

`runr::runWaterfall` runs its input tasks sequentially, passing each task's return value to the next task, and returns either a named list (on error `NULL`) or the value of a given callback.

:ocean: All tasks except the first must have at least one parameter.

```{r}
# chain/pipe consecutive returns
runr::runWaterfall(list(zoo,
                        base::factorial,  # reference names anyhow
                        runr::bind(Reduce, function(a, b) a + b)))  # binding
```

`runr::bind` takes a function object and a variable sequence of parameters as inputs and returns a closure with the given parameters bound to it.

***

## runRace

`runr::runRace` runs its input tasks parallel until the very first return of any of its tasks and returns either a named list (all `NULL` but one and on error `NULL`) or the value of a given callback.

```{r}
# see how return is variable due to instable time lags between child launches
runr::runRace(list(function() {Sys.sleep(11L); '1st first'}, 
                   function() {Sys.sleep(10L); '2nd first'}), 
              callback)
```

***

## runParallel

`runr::runParallel` runs its input tasks parallel until all complete and returns either a named list (on error `NULL`) or the value of a given callback.

```{r}
# callback
hireme <- function(err, d) {
  if (!is.null(err)) stop(err, err$task)  # check n go
  sprintf('dev: @chiefBiiko | hireable: %s%s | %s',
          as.character(d$function1$hireable), 
          d$function2, d$function3)
}
# see ya!
runr::runParallel(list(runr::bind(jsonlite::fromJSON, 
                                  'https://api.github.com/users/chiefBiiko'), 
                       runr::bind(strrep, '!', 10L),
                       function() gsub('[^3<]', '', '<kreuzberg36original>')), 
                  hireme)
```
